1-d Convex Elicitation Notes

### 2018-04-29 notes-1d/one-dim.tex
lots of new notes
Added proof of Lemma 2

\title{1-d Convex Elicitation Notes}
\date{\today}

@@

\begin{lemma}[Monotonicity] \label{lemma:monot}
  Consider a convex one-dimensional loss with $r \in \argmin_{z} \ell(z;p)$ and $r' \not\in \argmin_z \ell(z;p)$.
  If $r < r' \leq r''$ then
    \[ \ell(r';p) \leq \ell(r'';p) . \]
  The same holds if $r > r' \geq r''$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

>>>>

\title{1-d Convex Elicitation Notes}
\author{Bo?}
\date{\today}

@@

\begin{lemma}[Monotonicity] \label{lemma:monot}
  Consider a convex one-dimensional loss with $r \in \argmin_{z} \ell(z;p)$ and $r' \not\in \argmin_z \ell(z;p)$.
  If $r < r' \leq r''$ then
    \[ \ell(r';p) \leq \ell(r'';p) . \]
  The same holds if $r > r' \geq r''$.
\end{lemma}
\begin{proof}
  Since $\ell(r,\cdot)$ is a convex function in $r$, we know by Jensen's inequality that $\ell(\lambda r + (1-\lambda)r''; p) \leq \lambda \ell(r; p) + (1-\lambda) \ell(r''; p)$ for $\lambda \in [0,1]$.
  As we know $r < r' \leq r''$, we can write $r'$ as a convex combination of $r$ and $r''$: that is, $r' = \lambda r + (1-\lambda) r''$.
  By substitution, we then observe $\ell(r'; p) \leq \lambda \ell(r; p) + (1-\lambda) \ell(r''; p) < \lambda \ell(r'; p) + (1-\lambda) \ell(r''; p)$ for $\lambda \in (0,1]$, as $\ell(r;p) < \ell(r';p)$.
  With some simple manipulation, we then observe $\ell(r';p) \leq \ell(r'';p)$

\end{proof}
